\chapter{Problem Statement}
\label{chapter:ConfTask}
The objective of this project is to improve the configurability of the
Execution Manager as outlined in the diploma-thesis by Christian Motika\cite{cmot-dt} :
\begin{quote}
 \ac{KIEM} currently does not have a preference page to save
additional settings like DataComponent timeouts. Also execution schedulings
might be similar for a common diagram type.

It may improve the usability further to allow the user to customize execution
schedulings for specific diagram types. An interface for these kind of settings
could be realized as an Eclipse preference page.
\end{quote}

This task will be explained in more detail in this chapter. It will start by introducing 
solutions to the problem of how save the new configuration properties into the existing 
execution files. In addition the chapter will explain ways to enable the user to set up a 
series of default configurations. The last section of this chapter will explore 
possibilities of how to make it easier to load previously saved schedules.

\section{Configurations}
\label{section:ConfTaskConfig}
Currently every property in the Execution Manager has a hard coded default value. There is a text box
for setting the aimed step duration for the currently loaded execution file but that value
is lost once a new execution file is loaded.
To solve this problem an extension to the Execution Manager should attempt to provide the following:
\begin{enumerate}
 \item Find a way that execution files can store values like the aimed step duration and the timeout.
This mechanism should be implemented in a way that ensures that old files can be upgraded and new
files are still valid in instances of the Execution Manager that don't use the configuration plug-in.
 \item Find a way to load the configurations into the different parts of the Execution Manager as soon as an
execution file is loaded from the file system.
 \item Ensure that the user can edit all properties and maybe even create his own custom properties.
This should be implemented in a way that doesn't clutter up the current user interface too much.
\end{enumerate}

\subsection{Default Configuration}
\label{section:ConfTaskDefaultConfig}
\index{Default Configuration}
The different properties stored in each execution file might sometimes not suit the users current needs
and he might want to use a default value for some properties without having to manually set them
in each new configuration.
The solution could be implemented using the preference mechanism provided by Eclipse.
\begin{enumerate}
 \item There should be a way to set the default properties for all Execution Manager properties 
and possibly for user defined properties as well.
 \item It should be possible for the user to set up which of these properties should override 
the value stored in the execution file and which
should only be used if the execution file doesn't contain one.
\end{enumerate}

\section{Easier Configuration Loading}
\label{section:ConfTaskEasyLoading}
The last objective of this thesis is to make it easier to load execution files.
Currently all execution files are stored in the workspace at a place of the users choice. In a very
large workspace it can be very hard to find the execution file that you need for your current
simulation. The list of recently used documents that Eclipse provides is of little use since all
opened documents are placed there not just execution files.
This problem leads to the in the following tasks:
\begin{enumerate}
 \item Finding a way to track recently used execution files and make it easier for the user to
load them without the need to locate them inside his workspace.
 \item In addition to tracking recently used execution files the user might want to have a way to get a list
of execution files that work for the currently active editor. This list should be sorted with the most likely
candidates at the top to allow less experienced users to select an execution file that will most likely work.
\end{enumerate}
